### 2015-05-15 whoop.tex
fix

Symbolic verification of a pair of entry points works by (i) instrumenting each entry point with additional state to record locksets, and (ii) attempting to verify a sequential program that executes the instrumented entry points in sequence and then asserts, for each shared location, that the locksets for each entry point with respect to this location have a non-empty intersection.  Verification of the resulting sequential program can be undertaken using any sound method; in practice we employ the Boogie verification engine~\cite{barnett2006boogie}, which requires procedure specifications and loop invariants to be generated, after which verification conditions~\cite{barnett2005weakest} (VCs) are generated and discharged by an automated theorem prover.

>>>>

Symbolic verification of a pair of entry points works by (i) instrumenting each entry point with additional state to record locksets, and (ii) attempting to verify a sequential program that executes the instrumented entry points in sequence and then asserts, for each shared location, that the locksets for each entry point with respect to this location have a non-empty intersection.  Verification of the resulting sequential program can be undertaken using any sound method; in practice we employ the Boogie verification engine~\cite{barnett2006boogie}, which requires procedure specifications and loop invariants to be generated, after which verification conditions~\cite{barnett2005weakest} (VCs) are generated and discharged to an automated theorem prover.
